Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-02-24 doc/paper.Rmd
small change

## Motivation
Same source analyses are a major part of an Forensic Toolmark examiners job. In current practice firearm examiners  make these comparisons visually under a comparison microscope and make one of the following four conclusions: identification, inconclusive, elimination or unsuitable for examination \citet{afte-website-2}. These conclusions are made on the basis of "unique surface contours" of the two toolmarks being in "sufficient agreement" \citep{afte-toolmarks1998}. AFTE describes the term "sufficient agreement" as the possibility of another tool producing the markings under comparison, as practically impossible \citep{afte-toolmarks1998} \citep{afte-website}. \gk{Although, they go on to concede that the interpretation of the identification depends on the examiner and is  therefore subjective in nature. }

@@

\gk{\citep{afte-website} quotes sufficient agreement as "agreement of individual characteristics is of a quantity and quality that the likelihood another tool could have made the mark is so remote as to be considered a practical impossibility"}.} 
\gk{could not find the pdf for AFTE theory of identification as it relates to toolmarks pdf. I believe it is not available for free. But from the AFTE Journal the abstract was available which mentions the term " sufficient agreement" as quoted above. Currently the website seems like the most reliable way of quoting AFTE, i have checked other sources in both occasions where the website has been quoated above, like an FBI paper available at the FBI website and some non published but available pdf files in the AFTE website that have used these lines and quoted the AFTE journal. But since I cannot verify it in the Journal I have quoated the website.}
\gk{faden et al have not cited any paper that discusses the algorithm, i assume it was developed for the paper, the discussion of which is not as extensive as chumbley's. Its a variation of the chumbley method but from my understanding it is just the optimization step. and this paper came out much before the chumbley score.}

>>>>

## Motivation
Same source analyses are a major part of an Forensic Toolmark examiners job. In current practice firearm examiners  make these comparisons visually under a comparison microscope and make one of the following four conclusions: identification, inconclusive, elimination or unsuitable for examination \citet{afte-website-2}. These conclusions are made on the basis of "unique surface contours" of the two toolmarks being in "sufficient agreement" \citep{afte-toolmarks1998}. AFTE describes the term "sufficient agreement" as the possibility of another tool producing the markings under comparison, as practically impossible \citep{afte-toolmarks1998} \citep{afte-website}. \gk{Although, they go on to concede that the interpretation of the identification depends on the examiner and is  therefore subjective in nature.}

@@

\gk{\citep{afte-website} quotes sufficient agreement as "agreement of individual characteristics is of a quantity and quality that the likelihood another tool could have made the mark is so remote as to be considered a practical impossibility"} 
\gk{could not find the pdf for AFTE theory of identification as it relates to toolmarks pdf. I believe it is not available for free. But from the AFTE Journal the abstract was available which mentions the term " sufficient agreement" as quoted above. Currently the website seems like the most reliable way of quoting AFTE, i have checked other sources in both occasions where the website has been quoated above, like an FBI paper available at the FBI website and some non published but available pdf files in the AFTE website that have used these lines and quoted the AFTE journal. But since I cannot verify it in the Journal I have quoated the website.}
\gk{faden et al have not cited any paper that discusses the algorithm, i assume it was developed for the paper, the discussion of which is not as extensive as chumbley's. Its a variation of the chumbley method but from my understanding it is just the optimization step. and this paper came out much before the chumbley score.}
